Looking for CDI Bias: WG Comprehension

### 2021-07-07 02-preliminary-WGcomp.Rmd
fitting DIF sex to WG comprehension

---
title: "Looking for CDI Bias: WG Production"
author: "Nathan, George, and Mike"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

@@

```{r get-wordbank-items, eval=F, echo=F}
d_long_wg <- get_instrument_data(language="English (American)", form = "WG") %>%
  mutate(produces = as.numeric(value == "produces")) # we'll start with production
# yes = understands; no = does not understand/produce, produces = produces (and understands)

@@

save(d_mat, d_demo, en_wg, file=here("data/en_wg.Rdata"))
```

```{r load-data}
# load saved CDI:WG data
load(here("data/en_wg.Rdata")) # d_demo, d_mat, en_wg (items)

@@

save(file = here("data/eng_wg_mod_2pl.Rds"), "m1", "coefs_2pl") # "fscores_2pl",
```

@@

save(file = here("data/eng_wg_sex_slopes_invariant.Rds"), 
     mg2, m_sc2, mod_sc1, mod_fullconstrain)
```

```{r}
load(here("data/eng_wg_sex_slopes_invariant.Rds"))
load(here("data/eng_wg_mod_2pl.Rds"))

>>>>

---
title: "Looking for CDI Bias: WG Comprehension"
author: "Nathan, George, and Mike"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

@@

Let's do comprehension data.

```{r get-wordbank-items, eval=F, echo=F}
d_long_wg <- get_instrument_data(language="English (American)", form = "WG") %>%
  mutate(produces = as.numeric(value == "yes" | value == "produces")) # we'll start with production
# yes = understands; no = does not understand/produce, produces = produces (and understands)

@@

save(d_mat, d_demo, en_wg, file=here("data/en_wg_comp.Rdata"))
```

```{r load-data}
# load saved CDI:WG data
load(here("data/en_wg_comp.Rdata")) # d_demo, d_mat, en_wg (items)

@@

save(file = here("data/eng_wg_comp_mod_2pl.Rds"), "m1", "coefs_2pl") # "fscores_2pl",
```

@@

save(file = here("data/eng_wg_comp_sex_sexDIF.Rds"), 
     mg2, m_sc2, mod_sc1, mod_fullconstrain)
```

```{r}
load(here("data/eng_wg_comp_sex_sexDIF.Rds"))
load(here("data/eng_wg_comp_mod_2pl.Rds"))
